\bf Primal-dual algorithm for computing Nash equilibria in sequential games with imcomplete information

### 2015-05-31 nips2015.tex
ENH: more

and the dual LCP
\begin{equation}
  \begin{aligned}
    \text{maximize}-e_2^Tq,\hspace{.5em}\text{subject to }(y,q) \in
    \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}, -A^Tx - E_2^Tq \leq 0,
    E_1x = e_1, x \ge 0.
  \end{aligned}
  \label{eq:dual_pb}
\end{equation}
The vectors $p = (p_0, p_1, ..., p_{l_2 - 1}) \in \mathbb{R}^{l_2}$
and $q = (q_0, q_1, ..., q_{l_1 - 1}) \in \mathbb{R}^{l_1}$ are dual
variables. 
$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose
entries are $-1$, $0$ or $1$, and each $e_k$ is a vector of the form
$[1, 0, ..., 0]$. In this so-called \textit{sequence-form}
representation, the strategy profile of player $k$ is the polyhedron
\begin{equation}
  Q_k := \{z \in \mathbb{R}^n_+ |\text{ }E_kz = e_k\}
\label{eq:polyhedron}
\end{equation}
Note that $p^Te_1 = p_0$ and $q^Te_2 = q_0$ by definition of $e_1$ and
$e_2$. At a feasible point $(y, p, x, q)$, the \textit{duality gap}
$\mathcal{G}(y, p, x, q)$ of these primal-dual pair of LCPs is given
by\footnote{The inequality being due to \textit{weak duality}.}
\begin{equation}
  0 \le \mathcal{G}(y, p, x, q) := p_0 - (-q_0) = p_0 + q_0
  \label{eq:dgap}
\end{equation}

@@

Moreover, at equilibria, \textit{strong duality} holds and the value of the game equals $p_0 = -q_0$, i.e the duality gap $\mathcal{G}(y, p, x, q)$ defined in \eqref{eq:dgap} vanishes at equilibria.

@@

\begin{definition}(\textbf{Nash $\epsilon$-equilibria})
Given a small margin $\epsilon > 0$, a Nash $\epsilon$-equilibrium is a pair $(x^*, y^*)$ of realization plans such that there exists dual vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} such that the duality gap at $(y^*, p^*, x^*, q^*)$ doesn't exceed $\epsilon$. That is,
\begin{equation}
  0 \le \mathcal{G}(y^*, p^*, x^*, q^*) \le \epsilon
\label{eq:approx_pb}
\end{equation}
\end{definition}

\subsection{Precise statement of the problem}
The goal of this article is to device a simple algorithm which produces a Nash $\epsilon$-equilibrium after $\mathcal{O}(1/\epsilon)$ iterations.
%We first briefly introduce the sequence-form representation, and contrast it to the strategic-form representation. Then we state the Nash equilibrium problem for the sequence-form representation. Then in

@@

\section{Our contributions}
\label{sec:algo}
\subsection{Reformulation as a Generalized Saddle-point Problem (GSP)}
One cannot directly attack the LCPs \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} via a traditional primal-dual algorithm
(for example \cite{chambolle2010,chambolle2014ergodic}) because
computing the euclidean projections $\proj_{Q_k}$ is very difficult
(in fact, such subproblems would have to be solved
iteratively\footnote{An ``exception to the rule'' is the case where
  the $Q_k's$ are simplexes, so that the projections can be computed
  exactly using \cite{duchi2008efficient}.}). Also,
the primal-dual gap might explode even at ``nearly feasible'' points,
leaving a primal-dual algorithm with no clear on whether progress is
being made or not. So need to way to
\begin{itemize}
\item avoid having to compute the projections $\proj_{Q_k}$, and
\item cope  with infinite primal-dual gaps.
\end{itemize}

@@

\section{The algorithm}
%% According to Theorem \ref{thm:pd}, solving the Nash equilibrium LCPs
%% \eqref{eq:primal_pb}, \eqref{eq:dual_pb} is equivalent to solving the
%% saddle-point problem \eqref{eq:unconstrained_pb}. An attractive method
%% for such a saddle-point problem would be a primal-dual scheme, like
%% that developed in \cite[Algorithm 39]{chambolle2010}. 
%% Usually, to use a primal-dual algorithm, one needs a measure of the
%% ``quality'' of the current iterates as regards being the solution of
%% the saddle-point problem. A natural measure of this fittness is the
%% primal-dual gap, which measures defection from strong-duality.
%% However, the primal-dual gap in \eqref{eq:unconstrained_pb} can be
%% unbounded even at near feasible points.  is well-suited for

>>>>

and the dual LCP
\begin{equation}
  \begin{aligned}
    \text{maximize}-e_2^Tq,\hspace{.5em}\text{subject to }(y,q) \in
    \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}, -A^Tx - E_2^Tq \leq 0,
    E_1x = e_1, x \ge 0.
  \end{aligned}
  \label{eq:dual_pb}
\end{equation}
The vectors $p = (p_0, p_1, ..., p_{l_2 - 1}) \in \mathbb{R}^{l_2}$
and $q = (q_0, q_1, ..., q_{l_1 - 1}) \in \mathbb{R}^{l_1}$ are dual
variables. 
$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose
entries are $-1$, $0$ or $1$, and each $e_k$ is a vector of the form
$[1, 0, ..., 0]$. In this so-called \textit{sequence-form}
representation, the strategy profile of player $k$ is the polyhedron
\begin{equation}
  Q_k := \{z \in \mathbb{R}^n_+ |\text{ }E_kz = e_k\}
\label{eq:polyhedron}
\end{equation}
Note that $p^Te_1 = p_0$ and $q^Te_2 = q_0$ by definition of $e_1$ and
$e_2$. At a feasible point $(y, p, x, q)$, the \textit{primal-dual gap}
$\mathcal{G}(y, p, x, q)$ of these primal-dual pair of LCPs is given
by\footnote{The inequality being due to \textit{weak duality}.}
\begin{equation}
  0 \le \mathcal{G}(y, p, x, q) := p_0 - (-q_0) = p_0 + q_0
  \label{eq:dgap}
\end{equation}

@@

Moreover, at equilibria, \textit{strong duality} holds and the value of the game equals $p_0 = -q_0$, i.e the primal-dual gap $\mathcal{G}(y, p, x, q)$ defined in \eqref{eq:dgap} vanishes at equilibria.

@@

\begin{definition}(\textbf{Nash $\epsilon$-equilibria})
Given a $\epsilon > 0$, a Nash $\epsilon$-equilibrium is
a pair $(x^*, y^*)$ of realization plans such that there exists dual
vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} such that the primal-dual gap at $(y^*, p^*, x^*, q^*)$
doesn't exceed $\epsilon$. That is,

\begin{equation}
  0 \le \mathcal{G}(y^*, p^*, x^*, q^*) \le \epsilon
\label{eq:approx_pb}
\end{equation}
\end{definition}

\begin{definition}(\textbf{Nash $(\rho,\epsilon)$-equilibria})
Given $\rho > 0$ and $\epsilon > 0$, a Nash $(\rho,\epsilon$)-equilibrium is
a pair $(x^*, y^*)$ of realization plans such that there exists dual
vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} such that ...

\begin{equation}
  0 \le \mathcal{G}(y^*, p^*, x^*, q^*) \le \epsilon
\label{eq:approx_pb}
\end{equation}
\end{definition}

@@

\section{Reformulation as a Generalized Saddle-point Problem (GSP)}
\label{sec:gsp}
One cannot directly attack the LCPs \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} via a traditional primal-dual algorithm
(for example \cite{chambolle2010,chambolle2014ergodic}) because
computing the euclidean projections $\proj_{Q_k}$ is very difficult
(in fact, such subproblems would have to be solved
iteratively\footnote{An ``exception to the rule'' is the case where
  the $Q_k's$ are simplexes, so that the projections can be computed
  exactly using \cite{duchi2008efficient}.}). Also,
the primal-dual gap might explode even at ``nearly feasible'' points,
leaving a primal-dual algorithm with no clear on whether progress is
being made or not. So need to way to
\begin{itemize}
\item avoid having to compute the projections $\proj_{Q_k}$, and
\item cope  with infinite primal-dual gaps.
\end{itemize}

@@

\section{The algorithm}
\label{sec:algo}

%% According to Theorem \ref{thm:pd}, solving the Nash equilibrium LCPs
%% \eqref{eq:primal_pb}, \eqref{eq:dual_pb} is equivalent to solving the
%% saddle-point problem \eqref{eq:unconstrained_pb}. An attractive method
%% for such a saddle-point problem would be a primal-dual scheme, like
%% that developed in \cite[Algorithm 39]{chambolle2010}. 
%% Usually, to use a primal-dual algorithm, one needs a measure of the
%% ``quality'' of the current iterates as regards being the solution of
%% the saddle-point problem. A natural measure of this fittness is the
%% primal-dual gap, which measures defection from strong-duality.
%% However, the primal-dual gap in \eqref{eq:unconstrained_pb} can be
%% unbounded even at near feasible points.  is well-suited for
